---
title: "Assignment"

---

This is R markdown file for project 1. 

Read in data used for project. 

```{r}
data <- read.csv("activity.csv")
data$date <- as.POSIXct(data$date)
```

Calculate the total number of steps taken per day
Plot the total number of steps taken per day

```{r}
daySteps <- tapply(data$steps, data$date, sum, na.rm = TRUE)
png('plot1.png')
barplot(daySteps, xlab = 'Date', ylab = 'Number of Steps', main =  'Number of Steps per Day')
dev.off()
```

Show the summary of number of steps taken each day

```{r}
results <- summary(daySteps)
```

*Mean: `r results['Mean']`
*Median: `r results['Median']`

Time series plot of 5-minute interval 

```{r}
activityPattern <- aggregate(steps~interval, data, mean, na.rm=TRUE)
png('plot2.png')
plot(activityPattern, type="l", xlab = 'Steps', ylab = 'Interval', main = 'Time Series Plot')
dev.off()
```

5-minute interval contains maximum number of steps

```{r}
MostInterval <- data$interval[which.max(activityPattern$step)]
```

*maxInterval: `r MostInterval`

Number of NAs

```{r}
NumNa <- sum(is.na(data))
```

numberNAs: `r NumNa`

Filling missing data with daily average steps
```{r}
imputeData <- merge(data, activityPattern, by = 'interval')
imputeData <- imputeData[order(imputeData$date,imputeData$interval),] 
stepNA <- is.na(imputeData$steps.x)
imputeData$steps.x[stepNA] <- imputeData$steps.y[stepNA]
imputeData <- imputeData[,1:3]
names(imputeData)[2] <- 'steps'

```

Plot to show number of steps taken each day

```{r}
filledDaySteps <- tapply(imputeData$steps, imputeData$date, sum)
png('plot3.png')
barplot(filledDaySteps, xlab = 'Date', ylab = 'Number of Steps', main =  'Number of Steps per Day')
dev.off()
```

Show the summary of number of steps taken each day

```{r}
filledSum <- summary(filledDaySteps)
```

*Mean: `r filledSum['Mean']`
*Median: `r filledSum['Median']`

Generate daytype as factor, and plot steps by 'weekday' and 'weekend'

```{r}
imputeData$daytype <- 'weekday'
weekenddays <- weekdays(as.Date(imputeData$date)) %in% c('Saturday', 'Sunday')
imputeData$daytype[weekenddays] <- 'weekend'
imputeData$daytype <- as.factor(imputeData$daytype)

daySteps3 <- aggregate(steps ~ interval + daytype, imputeData, mean)
library(lattice)
png('plot4.png')
plot <- xyplot(daySteps3$steps ~ interval | daytype, daySteps3, type='l', layout = c(1,2))
print(plot)
dev.off()
```